### 2015-07-02 narrative/intro.tex
cleaned up table a bit. Will add things later.

Our proposal will be responsive to theme 2 in the call, and we summarize them in the following table.
\begin{table}[htbp]
\vspace{2ex}
\begin{center}
\begin{tabular}{ | p {0.2cm} | p{5cm} | p{7.5cm} | p{1.6cm} |}\hline
\multicolumn{2}{|c|}{\bf Call area} & \multicolumn{1}{|c|}{\bf Relevant S2E2 work} & \multicolumn{1}{|c|}{\bf See} \\\hline\hline
%\multicolumn{2}{|c|}{Collaboration} & 
\multicolumn{2}{|p {2.4cm}|}{Approaches to improve the ability of SSIO software to support checkpoint/restart;} & 
General piece we are doing for this... & 
\S\ref{sec:?}, \S\ref{sec:??}, \\\hline
1 & Data \hspace{1cm} abstractions &What will we do& \S\ref{sec:?}, \S\ref{sec:?}, \S\ref{sec:?} \\\hline
2 & Mapping science data models onto hierarchical storage &What we are doing & \S\ref{sec:?}, \S\ref{sec:?} \\\hline
3 & Mechanisms for data movement across the storage hierarchy  & what are we doing. & \S\ref{sec:?} \\\hline
4 &  Extend the interaction of IO middleware with the resource management system & What we are doing & \S\ref{sec:?}, \S\ref{sec:?}  \\\hline
5 & Design and implement of IO middleware architectures  &What we are doing & \S\ref{sec:?}, \S\ref{sec:?}, \S\ref{sec:?} \\
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

Our proposal will be responsive to theme 2 in the call, and we summarize them in the following table.
\begin{table}[htbp]
\vspace{2ex}
\begin{center}
\begin{tabular}{ | p {0.2cm} | p{5cm} | p{7.5cm} | p{1.6cm} |}\hline
\multicolumn{2}{|c|}{\bf Call area} & \multicolumn{1}{|c|}{\bf Relevant S2E2 work} & \multicolumn{1}{|c|}{\bf See} \\\hline\hline
%\multicolumn{2}{|c|}{Collaboration} & 
\multicolumn{2}{|p {5.5cm}|}{Approaches to improve the ability of SSIO software to support checkpoint/restart;} & 
General piece we are doing for this... & 
\S\ref{sec:?}, \S\ref{sec:??}, \\\hline
1 & Data abstractions & What will we do & \S\ref{sec:?}, \S\ref{sec:?}, \S\ref{sec:?} \\\hline
2 & Mapping science data models onto hierarchical storage & What we are doing & \S\ref{sec:?}, \S\ref{sec:?} \\\hline
3 & Mechanisms for data movement across the storage hierarchy & what are we doing. & \S\ref{sec:?} \\\hline
4 &  Extend the interaction of IO middleware with the resource management system & What we are doing & \S\ref{sec:?}, \S\ref{sec:?}  \\\hline
5 & Design and implement of IO middleware architectures  & What we are doing & \S\ref{sec:?}, \S\ref{sec:?}, \S\ref{sec:?} \\
\hline
\end{tabular}
\end{center}
\end{table}
